---
header-includes:
- usepackage{titling}
- pretitle{\begin{center}\LARGE\includegraphics[width=6cm]{./PW Logo files/PNG (raster)/large-png-pacific-wild-logo/pw-logo-dark-transparent-bg@2x.png}\\[\bigskipamount]}
- posttitle{\end{center}}
output: html_document
always_allow_html: yes
---
# Economic Value of Pacific Herring in the Strait of Georgia  
Tim Cashion  
`r format(Sys.time(), '%B %d, %Y')`  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
library(knitr)
library(tidyverse)
library(hrbrthemes)
library(bookdown)
library(plotly)
library(kableExtra)
#library(Cairo)
source("./R/cpi_function.R")
cpi <- read_csv("./Data/Canadian_CPI.csv") %>% 
  mutate(base_year=2002) %>% 
  select(-InflationRate)
cpi_2015 <- inflation_adjust(cpi, 2015) %>% 
  rename(Year=year)
#theme_set(theme_ipsum()) # Doesn't work on PC because it's missing Arial Narrow font.
theme_set(theme_ipsum_rc() + 
            theme(text=element_text(family="Alegreya Sans"),
                  axis.title.x = element_text(family="Alegreya Sans"),
                  axis.title.y = element_text(family="Alegreya Sans")
                  ))
plot_font <- list(
  family = c("Alegreya Sans", "Open Sans"),
  familysrc = "http://fonts.googleapis.com/css?family=Alegreya+Sans")


number_call <- function(num, decimals){
  x <- prettyNum(num, big.mark = ",", small.mark = ".", digits=decimals) 
  return(x)
}

short_to_metric_multiplier <- 2000 /2204.623


```



```{r licence-number, echo=F, warning=F, message=F, fig.cap="Total herring licenses by fishery type"}
areas <- c("Strait of Georgia", "Prince Rupert")

net_change_area_licences <- read.csv("./Data/net_change_area_licences.csv")
herring_lic_area_plot <- net_change_area_licences %>% 
  filter(AREA %in% areas) %>% 
  rename(`Source Area`= LagAREA) %>% 
  ggplot(aes(x=Year, y=NetChange, color=`Source Area`)) +
  geom_line() +
  ylab("") +
  #ylab("Number of herring licences switching to new area") + 
  labs(color="Area") + 
  scale_color_ipsum() + 
  facet_wrap(~AREA, ncol=1) + 
  #theme(plot.title = element_text(hjust = 0.5)) + 
  NULL 
# ggsave("./Images/Net licence movement for the two main roe fishing areas.tiff", dpi=300)

ggplotly(herring_lic_area_plot) %>% 
  layout(font=plot_font) %>% 
  layout(yaxis = list(title = paste0(c("Number of herring licences switching to new area                ",
                                         rep("\n", 1)),
                                       collapse = "")))


